Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-14 code/rmarkdown/figures.Rmd
+ bug fix in figures
Former-commit-id: 18a72705e0a71d4a5aa07b57025495f472f8c877
+ another bug fix
Former-commit-id: c3da4e8802ccbdf0377c42e3e47fa22c14a116aa
+ fixes to docs + increased iterations for bayescan + fixed bug in pcadapt analysis + assorted changes to main and SI figures + added funcionality to push and pull ms from cb

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='Planning unit selection frequencies. The first row of panels (a--c) show single-species prioritizations generated assuming equal costs. The second row of panels (d--f) show single-species prioritizations generated using opportunity costs. The third row of panels (g--i) show multi-species prioritizations generated assuming equal costs. The fourth row of panels (j--l) show multi-species generated using opportunity costs. The left column of panels (a, d, g, j) show prioritizations generated using only amount-based targets. The middle column of panels (b, e, h, k) show prioritizations generated using amount- and surrogate-based targets. The right column of panels (c, f, i, l) show prioritizations generated using amount- and genetic-based targets. The color of each planning unit indicates its selection frequency. Note that the selection frequencies for the single-species prioritizations (panels a--f) are based on their average frequency among multiple prioritizations generated for each species. The selection frequences for the multi-species prioritizations (pabels g--l) are based on the optimal pioritization (thus they are all either zero or one).'}

@@

for (i in seq_along(single.spp.prioritisations.cost[[1]]))

@@

			levels=c("Single-species\n(equal costs)", "Single-species\n(opportunity costs)"

@@

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=genetic.held),
		data=scenario.DF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=0.6, y=1.15, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=6.5, fig.cap='Planning unit selection frequencies. The first row of panels (a--c) show single-species prioritizations generated assuming equal costs. The second row of panels (d--f) show single-species prioritizations generated using opportunity costs. The third row of panels (g--i) show multi-species prioritizations generated assuming equal costs. The fourth row of panels (j--l) show multi-species generated using opportunity costs. The left column of panels (a, d, g, j) show prioritizations generated using only amount-based targets. The middle column of panels (b, e, h, k) show prioritizations generated using amount- and surrogate-based targets. The right column of panels (c, f, i, l) show prioritizations generated using amount- and genetic-based targets. The color of each planning unit indicates its selection frequency. Note that the selection frequencies for the single-species prioritizations (panels a--f) are based on their average frequency among multiple prioritizations generated for each species. The selection frequences for the multi-species prioritizations (pabels g--l) are based on the optimal pioritization (thus they are all either zero or one).'}

@@

for (i in seq_along(single.spp.prioritisations.with.cost[[1]]))

@@

			levels=c("Single-species\n(equal costs)", "Single-species\n(opportunity costs)",

@@

scenario.SDF <- scenario.DF %>% 
	group_by(Prioritisation, Context, Metric, Species) %>% 
	summarize(genetic.held=mean(genetic.held, na.rm=TRUE)) %>%
	data.frame()

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=genetic.held),
		data=scenario.SDF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=0.6, y=1.15, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		geom_abline(slope=0, color='red', linetype='dashed',
			intercept=rapr.params.LST[[MODE]]$scenario.analysis$genetic.target) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```

### 2016-05-14 code/rmarkdown/supporting_information.Rmd
+ fixes to docs + increased iterations for bayescan + fixed bug in pcadapt analysis + assorted changes to main and SI figures + added funcionality to push and pull ms from cb

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=12),
			panel.margin.x=unit(1, 'lines')) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		geom_point(fill='transparent') +
		suppressWarnings(stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, fill='blue', alpha=0.8)) +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=5, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=12),
			panel.margin.x=unit(1, 'lines')) +
		xlab('Geographic variation secured (%)') +
		ylab('Neutral genetic variation secured (%)') +
		geom_point(fill='transparent') +
		suppressWarnings(stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, fill='blue', alpha=0.8)) +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=5, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

>>>>

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=12),
			panel.margin.x=unit(1, 'lines')) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		geom_point(fill='transparent') +
		suppressWarnings(stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, fill='blue', alpha=0.8)) +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=8, color='darkred') +
		facet_wrap(~ Species, ncol=4)
)
```

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=12),
			panel.margin.x=unit(1, 'lines')) +
		xlab('Geographic variation secured (%)') +
		ylab('Neutral genetic variation secured (%)') +
		geom_point(fill='transparent') +
		suppressWarnings(stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, fill='blue', alpha=0.8)) +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=8, color='darkred') +
		facet_wrap(~ Species, ncol=4)
)
```
